\begin{thebibliography}{999}

\bibitem{1} Christensen, Bo Hjort.(2003). \textit{Effektiv anvendelse av IKT : elektronisk forretningsdrift}. Oslo : SND, BIT-programmet.

\bibitem{} Sanders, James. (2014). Hybrid cloud: What it is, why it matters. \textit{ZDnet}. Hentet fra: http://www.zdnet.com/article/hybrid-cloud-what-it-is-why-it-matters/

\bibitem{} Kirsch, Brian. (2015). 6 Hybrid Cloud Providers Compared. \textit{Tom's IT Pro}. Hentet fra: http://www.tomsitpro.com/articles/hybrid-cloud-providers-comparison,2-841.html

\bibitem{} Warner, Tim. (2015). Microsoft Nano Server: Everything you need to know. \textit{Pluralsight}. Hentet fra: https://www.pluralsight.com/blog/it-ops/microsoft-nano-server-announced. 

\bibitem{} Laudon, Kenneth C., \& Laudon, Jane P.(2016). \textit{Management Information Systems, Managing the Digital Firm}.Pearson Education.

\bibitem{} Winslow, Dana. (2016). \textit{Why You Need a Local Testing Server (and How To Do It)}. Hentet fra: http://www.dwuser.com/education/content/why-you-need-a-testing-server-and-how-to-do-it/

\bibitem{} Ramachandran, Udaiappa. (2013). \textit{The Pros and Cons of Cloud Storage}.
Hentet fra: http://www.episerver.com/learn/resources/blog/udaiappa-ramachandran/the-pros-and-cons-of-cloud-storage/

\bibitem{} Davis, Kevin. (2014). \textit{Pros and Cons: Digging into Amazon Web Services}
Hentet fra: https://npifinancial.com/blog/pros-and-cons-digging-into-amazon-web-services/

\bibitem{} Vaughan-Nichols, Steven J. (2015). \textit{How Amazon Web Services crashed and rose again}
Hentet fra: http://www.zdnet.com/article/how-amazon-web-services-crashed-and-rose-again/

\bibitem{} Hambrick, Scott. (2015). \textit{Amazon Web Services Storage: Pros and Cons for Document Management}
Hentet fra: https://www.datastorageinc.com/blog/amazon-web-services-storage-pros-and-cons-for-document-management

\bibitem{} Hernandez, Pedro. (2016). \textit{Microsoft Azure Flaw Exposed RHEL Virtual Machines to Hacking Risk}
Hentet fra: http://www.networkworld.com/article/2224155/microsoft-subnet/microsoft-admits-to-being-hacked-too.html

\bibitem{} Smith, Ms. (2013, 25.04). Microsoft admits to being hacked too. \textit{Networkworld}
Hentet fra: http://www.networkworld.com/article/2224155/microsoft-subnet/microsoft-admits-to-being-hacked-too.html

\bibitem{} Shields, Anna. (2014). \textit{Why EMC, VMware, and Pivotal form a unique business model}
Hentet fra: http://marketrealist.com/2014/08/why-emc-vmware-and-pivotal-form-a-unique-business-model/

\bibitem{} Goldstein, Phil. (2017). Microsoft Warns that Virtual Machines Could Be Turned into Botnets. \textit{Biztechmagazine}. 
Hentet fra: http://www.biztechmagazine.com/article/2017/01/microsoft-warns-hacked-virtual-machines-are-very-real-threat

\bibitem{} Millman, Rene. (2016). Microsoft update left Azure Linux virtual machines open to hacking. \textit{SC Magazine UK}. 
Hentet fra: https://www.scmagazineuk.com/microsoft-update-left-azure-linux-virtual-machines-open-to-hacking/article/575472/

\bibitem{} Davis, Kevin. (2014). \textit{Pros and Cons: Digging into Amazon Web Services}. 
Hentet fra: https://npifinancial.com/blog/pros-and-cons-digging-into-amazon-web-services/

\paragraph{}\textbf{Bilder:}

\bibitem{}Msazurelogo. Hentet fra https://www.cristie.com/move/clonemanager-in-microsoft-azure/

\bibitem{} Amazon Web Services Immersion Day. Hentet fra https://bruintech.ucla.edu/events/2016-06-16/amazon-web-services-immersion-day

\bibitem{}Roadmap. Hentet fra http://www.cbronline.com/news/cloud/google-reveals-hybrid-cloud-plans-with-openstack-4863087/

\bibitem{} StorSimple. 
Hentet fra: https://azurecomcdn.azureedge.net/cvt-5d7b29713a4471c09f76f0526e9a341f048cd34f90636a43a421f075efb78f10/images/page/services/storsimple/diagram.png

\bibitem{}VMware. Hentet fra http://www.stablenet.net/solutions/cloud-computing/hybrid-cloud/

\bibitem{}Dataencryption. Hentet fra https://docs.microsoft.com/en-us/azure/storsimple/storsimple-security

\bibitem{}Hybrid Cloud. Hentet fra http://www.zdnet.com/article/vmwares-vision-and-roadmap-for-hybrid-cloud/
\end{thebibliography}